Exception Handling Bug Hazards in Android

### 2015-10-09 SPRINGER_JOURNAL/msr_journal.tex
typo
typos

%Android, the leading plaform for mobile applications~\cite{gartner} (thanks to its open-source 
%model and hardware partners like Samsung, HTC, Motorola, Asus besides Nexus Google's
% own device)  reuses the embedded Java exception model to detect and handle 
% exceptional conditions.

@@

Our study focuses on open-source apps, since the information needed to perform our study
cannot be retrieved from commercial apps, whose issue report systems and 
source codes are generally not publicly available. 
Open source Android open-source apps have also been the 
target of other research~\cite{Linar13,Ruiz12} addressing the \emph{reuse} and API stability.

@@

\emph{\textbf{Exception Signaler Analysis.}}
This module is responsible for classifying each signaler according 
to its origin (i.e., Android Application Framework, Android Libcore, Application, Library). 
Table~\ref{tab:signalers} presents the heuristics adopted in this classification.
To conduct this classification, we provide this module with the information
comprising all Java packages that compose: the Android Plaform;
 the Android Libcore; and each analyzed Application. To discover the packages for the first two origins
we can use the Android specification.
To discover the packages for the third origin, the application itself, this module
extracts the manifest files of each Android app, which defines the main packages that the applications consist of.
 If this file is not available, the tool recursively analyzes the 
structure of source-code directories composing the appm filtering out the cases in which the application also includes the source code of reused libraries.
Then, based on this information and using pattern matching 
between the signaler name and the packages, this module identifies 
the origin of the exception signalers.

@@

\finding{Almost two thirds of all crashes come from runtime
  exceptions. Most of these originate from the application layer.}

@@

Developers were also asked to rank the main causes of crashes. Approximately 68\% of the respondents ranked the exceptions signaled by programming logic mistakes, e.g. NullPointerExceptions, as the Top 1 and Top 2 cause of crashes, as illustrated in Figure~\ref{figure:ranking}. In our mining study the exceptions signaled due to programming logic mistakes (java.lang and util) where the causes of 52.0\% of the exception stack traces found. Hence, the developers perspective is aligned with what was revealed in mining study.
%[width=.9\hsize]
\begin{figure*} 
\centering \includegraphics[scale=0.60]{charts/ranking.png}
\caption{Developers perspectives on the main causes of crashes.}\label{fig:ranking} 
\end{figure*}

@@

\textit{Analysis and Use of Stack Trace Information.} Several papers have
investigated the use of stack trace information to support: bug classification
and clustering~\cite{wang2013improving, kim2011crash, dhaliwal2011classifying},
fault prediction models~\cite{kim2013predicting}, automated
bug fixing tools~\cite{sinha2009fault} and also the analysis of Android APIs~\cite{kechagia2014}. 
Kim et al.~\cite{kim2011crash} use an
aggregated form of multiple stack traces available in crash reports to detect
duplicate crash reports and to predict if a given crash will be fixed. Dhaliwal
et al.~\cite{dhaliwal2011classifying} proposed a crash grouping approach that
can reduce bug fixing time in approximately 5\%. Wang et
al.~\cite{wang2013improving} propose an approach to identify correlated crash
types and describe a fault localization method to locate and rank files related
to the bug described on a stack trace. Schroter et al.~\cite{schroter2010stack}
conducted an empirical study on the usefulness of stack traces for bug fixing
and showed that developers fixed the bugs faster when failing stack traces were
included on bug issues.  In a similar study, Bettenburg et
al.~\cite{bettenburg2008makes} identify stack traces as the second most stack
trace feature for developers.  Sinha et al.~\cite{sinha2009fault} proposed an
approach that uses stack traces to guide a dataflow analysis for locating and
repairing faults that are caused by the implicitly signaled exceptions. Kim
at al.~\cite{kim2013predicting} proposed an approach to predict the
crash-proneness of methods based information extracted from stack traces and
methods' bytecode operations.  They observed that most of the stack traces were
related to NullPointerException and other implicitly thrown exceptions had
the higher prevalence on the analyzed set of stacks. Kechagia and Spinellis~\cite{kechagia2014}
examined the stack traces embedded on crash reports sent by 1,800 Android apps 
to a crash report management service (i.e., BugSense). They found that 19\% of such stack traces
were caused by unchecked and undocumented exceptions thrown by methods defined on 
Android API (level 15). Our work differs from Kechagia and Spinellis since it is based on
stack traces mined from issues reported by open source developers on GitHub and Googlecode.  
Moreover, our study mapped the origin of each exception 
(i.e., libraries, the Android platform or the application itself) and investigated
the adoption of best practices based on the analysis of stack trace information.
Our work also identified the type of each exception mined from issues
(classifying them as Error, Runtime or Checked) based on the source code
analysis of the exception hierarchy and analized the exception wrappings that can 
happen during the exception propagation.  Such analysis revealed intriging 
\emph{bug hazards} such as the cross-type exception wrappings not discussed in previous works.

>>>>

%Android, the leading platform for mobile applications~\cite{gartner} (thanks to its open-source 
%model and hardware partners like Samsung, HTC, Motorola, Asus besides Nexus Google's
% own device)  reuses the embedded Java exception model to detect and handle 
% exceptional conditions.

@@

Our study focuses on open-source apps, since the information needed to perform our study
cannot be retrieved from commercial apps, whose issue report systems and 
source codes are generally not publicly available. 
Open source Android open-source apps have also been the 
target of other research~\cite{Linar13,Ruiz12} addressing \emph{reuse} and API stability.

@@

\emph{\textbf{Exception Signaler Analysis.}}
This module is responsible for classifying each signaler according 
to its origin (i.e., Android Application Framework, Android Libcore, Application, Library). 
Table~\ref{tab:signalers} presents the heuristics adopted in this classification.
To conduct this classification, we provide this module with the information
comprising all Java packages that compose: the Android Platform;
 the Android Libcore; and each analyzed Application. To discover the packages for the first two origins
we can use the Android specification.
To discover the packages for the third origin, the application itself, this module
extracts the manifest files of each Android app, which defines the main packages that the applications consist of.
 If this file is not available, the tool recursively analyzes the 
structure of source-code directories composing the appm filtering out the cases in which the application also includes the source code of reused libraries.
Then, based on this information and using pattern matching 
between the signaler name and the packages, this module identifies 
the origin of the exception signalers.

@@

\finding{Almost 65\% of all crashes come from runtime
  exceptions. Approximately 47\% of these originate from the application layer.}

@@

Developers were also asked to rank the main causes of crashes. Approximately 68\% of the respondents ranked the exceptions signaled by programming logic mistakes, e.g. NullPointerExceptions, as the Top 1 and Top 2 cause of crashes, as illustrated in Figure~\ref{fig:ranking}. In our mining study the exceptions signaled due to programming logic mistakes (java.lang and util) where the causes of 52.0\% of the exception stack traces found. Hence, the developers perspective is aligned with what was revealed in mining study.
%[width=.9\hsize]
\begin{figure*} 
\centering \includegraphics[scale=0.60]{charts/ranking.png}
\caption{Developers perspectives on the main causes of crashes.}\label{fig:ranking} 
\end{figure*}

@@

\textit{Analysis and Use of Stack Trace Information.} Several papers have
investigated the use of stack trace information to support: bug classification
and clustering~\cite{wang2013improving, kim2011crash, dhaliwal2011classifying},
fault prediction models~\cite{kim2013predicting}, automated
bug fixing tools~\cite{sinha2009fault} and also the analysis of Android APIs~\cite{kechagia2014}. 
Kim et al.~\cite{kim2011crash} use an
aggregated form of multiple stack traces available in crash reports to detect
duplicate crash reports and to predict if a given crash will be fixed. Dhaliwal
et al.~\cite{dhaliwal2011classifying} proposed a crash grouping approach that
can reduce bug fixing time in approximately 5\%. Wang et
al.~\cite{wang2013improving} propose an approach to identify correlated crash
types and describe a fault localization method to locate and rank files related
to the bug described on a stack trace. Schroter et al.~\cite{schroter2010stack}
conducted an empirical study on the usefulness of stack traces for bug fixing
and showed that developers fixed the bugs faster when failing stack traces were
included on bug issues.  In a similar study, Bettenburg et
al.~\cite{bettenburg2008makes} identify stack traces as the second most stack
trace feature for developers.  Sinha et al.~\cite{sinha2009fault} proposed an
approach that uses stack traces to guide a dataflow analysis for locating and
repairing faults that are caused by the implicitly signaled exceptions. Kim
at al.~\cite{kim2013predicting} proposed an approach to predict the
crash-proneness of methods based information extracted from stack traces and
methods' bytecode operations.  They observed that most of the stack traces were
related to NullPointerException and other implicitly thrown exceptions had
the higher prevalence on the analyzed set of stacks. Kechagia and Spinellis~\cite{kechagia2014}
examined the stack traces embedded on crash reports sent by 1,800 Android apps 
to a crash report management service (i.e., BugSense). They found that 19\% of such stack traces
were caused by unchecked and undocumented exceptions thrown by methods defined on 
Android API (level 15). Our work differs from Kechagia and Spinellis since it is based on
stack traces mined from issues reported by open source developers on GitHub and Googlecode.  
Moreover, our study mapped the origin of each exception 
(i.e., libraries, the Android platform or the application itself) and investigated
the adoption of best practices based on the analysis of stack trace information.
Our work also identified the type of each exception mined from issues
(classifying them as Error, Runtime or Checked) based on the source code
analysis of the exception hierarchy and analized the exception wrappings that can 
happen during the exception propagation.  Such analysis revealed intriguing 
\emph{bug hazards} such as the cross-type exception wrappings not discussed in previous works.
